---
title: "Demonstration of worcs"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
library("ggplot2")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
load_data()
knitr::opts_chunk$set(echo = FALSE) # TRUE = includes code
```

## Testing: descriptive statistics

```{r}
# Descriptive statistics
res_desc <- descriptives(df)
write.csv(res_desc, "res_desc.csv", row.names = FALSE)
knitr::kable(res_desc)
```

## Testing: simple regression model

```{r}
# Simple model
mod <- lm(bill_length_mm ~ species, data = df)
res_mod <- summary(mod)
write.csv(res_mod$coefficients, "res_coef.csv", row.names = FALSE)
knitr::kable(res_mod$coefficients, caption = "Regression coefficients")
```


This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.2, @vanlissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency.

This is an example of a non-essential citation [@vanlissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data.-->
`r notify_synthetic()`
